ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-06 paper/paper.tex
update

We only applied stacking on task 2 as task 1 is too compute-intensive.
We tried two stacking method seperately:
\begin{enumerate}
 \item 2-folds stacking split by two different time frame

 \item 10-folds stacking after merging two time frame
\end{enumerate}

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. It provides out-of-period stacking feature split by time, which is useful to avoid overfitting.

 \item Both stacking provides improvement on local CV, but 10 folds show discrepancy betweem CV and 30\% of testing data.
\end{enumerate}

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one algorithm.
Since we only used XGboost here, we tried to compensate this by building several stacking features using randomized parameters to achieve diversification.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=120mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the beginning and ranked parameter combinations based on Cross Validation.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best Cross Validation.

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample of data & [0.7, 0.8, 0.9, 1] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

We only applied stacking on task 2 but not task 1.
We tried two stacking method seperately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

 \item Stratified 10-folds stacking after merging two time frames
\end{enumerate}

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. If folds are split by time,
  stacking feature is built based on information from different time period, which is useful to avoid overfitting.

 \item Both stacking provides improvement on local CV, but 10 folds show discrepancy between CV and 30\% of testing data.
\end{enumerate}

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one algorithm.
Since we only used XGboost here, we compensated this by building several stacking features using randomized parameters to achieve diversification.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=115mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the beginning and ranked parameter combinations based on Cross Validation.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best Cross Validation result.

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample ratio of data when constructing each tree & [0.7, 0.8, 0.9, 1] & 1 \\
    $gamma$ & Minimum loss reduction required to make a further partition & [0, 0.025, 0.05, 0.1, 0.3] & 0 \\
    $min\_child\_weight$ & minimum sum of instance weight (Hessian) required to make a further partition & [1, 3, 5, 7] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}
